Excel fun

### 2022-07-16 Excel fun.Rmd
Excel function. Visualisation.

## Final final?
```{r}
excel <- read_excel("Data/OPXfinans_final.xlsx")
excel <- clean_names(excel)

@@

excel
```

>>>>

## Final final?
```{r}
excel <- read_excel("Data/OPXfinans_final.xlsx")
excel <- clean_names(excel)
excel

excel2

@@

excel
read_excel("Data/OPXfinans_final.xlsx") |> 
  mutate(
    Value = Value * 1000
  )

## Function
```{r}
widen_excel <- function(file){
  require(readxl)
  read_excel(file) |> 
    mutate(
      Value = Value * 1000
    ) |> 
  unite(
    entry, c(Category, Name), sep = "_"
  ) |> 
  select(-`Sub-category`) |> 
  pivot_wider(names_from = entry, values_from = Value) |> 
  clean_names()
}

widen_excel("Data/OPXfinans_final.xlsx")
```
